---
title: "STA 32 - HW 4"
author: "HANGSHI JIN"
output: html_document
---
  
### Problem I
### (a)
```{r, echo = FALSE}
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
sum(one.student == "NT")
```

### (b)
```{r, echo = FALSE}
n = 1000000
many.num.noturn = sapply(1:n,function(i){
	the.sample = sample( c("HW","None"), 40, replace = TRUE, prob = c(0.95,0.05))
	num.noturn = sum(the.sample == "None")
	return(num.noturn)
})
hist(many.num.noturn)
```

### (c)
```{r, echo = TRUE}
#No, it is not symmetric since the histogram shows.
```

### (d)
```{r, echo = FALSE}
n = 1000000
many.num.noturn = sapply(1:n,function(i){
	the.sample = sample( c("HW","None"), 40, replace = TRUE, prob = c(0.95,0.05))
	num.noturn = sum(the.sample == "None")
	return(num.noturn)
})
table(many.num.noturn)
```
#2 is the most frequent occuring number.

### Problem II
### (a)
```{r, echo = FALSE}
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
})
A = sum(many.students == "NT")
v.return = c(A/n,sd(many.students == "NT"))
names(v.return) = c("mean","standard deviation" )
v.return
```

### (b)
```{r, echo = FALSE}
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
  A = sum(one.student == "NT")
  return(A)
  })
sum(many.students == 0)/n
```

### (c)
```{r, echo = FALSE}
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
  A = sum(one.student == "NT")
  return(A)
  })
A = sum(many.students == 0)
B = sum(many.students == 1)
1-((A + B)/n)
```

### (d)
```{r, echo = FALSE}
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
  A = sum(one.student == "NT")
  return(A)
  })
median(many.students)
```

### Problem III
### (a)
```{r, echo = FALSE}
lynx = as.numeric(lynx)
hist(lynx)
v.return = c(mean(lynx),var(lynx))
names(v.return) = c("mean","variance")
v.return
```
#This data does not look normally distributed.

### (b)
```{r, echo = FALSE}
lynx = as.numeric(lynx)
the.sample = sample(lynx,10)
mean(the.sample)
```

### (c)
```{r, echo = FALSE}
n = 1000000
many.samples = sapply(1:n, function(i){
  lynx = as.numeric(lynx)
  the.sample = sample(lynx,10)
  A = mean(the.sample)
  return(A)
})
v.return = c(mean(many.samples),sd(many.samples))
names(v.return) = c("mean","standard deviation")
v.return
```

### (d)
```{r, echo = FALSE}
lynx = as.numeric(lynx)
n = 1000000
many.samples = sapply(1:n, function(i){
  lynx = as.numeric(lynx)
  the.sample = sample(lynx,10)
  A = mean(the.sample)
  return(A)
})
B = mean(lynx)
C = sd(lynx)
v.return = c(abs(B - mean(many.samples)),abs(C - sd(many.samples)))
names(v.return) = c("difference in mean","difference in standard deviation")
v.return
```

### Problem IV
### (a)
```{r, echo = FALSE}
n = 1000000
many.samples = sapply(1:n, function(i){
  lynx = as.numeric(lynx)
  the.sample = sample(lynx,10)
  A = mean(the.sample)
  return(A)
})
hist(many.samples)
```

#Less skewness

### (b)
```{r, echo = FALSE}
lynx = as.numeric(lynx)
the.sample = sample(lynx,50)
C = mean(the.sample)
D = sd(the.sample)
v.return = c(C,D)
names(v.return) = c("mean","standard deviation")
v.return
```

### (c)
```{r, echo = FALSE}
lynx = as.numeric(lynx)
n = 1000000
many.samples1 = sapply(1:n, function(i){
  the.sample1 = sample(lynx,50)
  A = mean(the.sample1)
  return(A)
})
v.return1 = c(mean(many.samples1),sd(many.samples1))
names(v.return1) = c("mean","standard deviation")
v.return1
many.samples2 = sapply(1:n, function(i){
  the.sample2 = sample(lynx,10)
  B = mean(the.sample2)
  return(B)
})
v.return2 = c((mean(many.samples1) - mean(many.samples2)),(sd(many.samples1) - sd(many.samples2)))
names(v.return2) = c("difference in mean","difference in standard deviation")
v.return2
```
#mean stays approximately the same while standard deviation decreases dramatically.

### (d)
```{r, echo = FALSE}
lynx = as.numeric(lynx)
n = 1000000
many.samples1 = sapply(1:n, function(i){
  the.sample1 = sample(lynx,50)
  A = mean(the.sample1)
  return(A)
})
hist(lynx)
```

#the slope of the histogram is decreasing. Therefore, the shape is like a mountain from the top to the bottom.

## APPENDIX OF CODE
```
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
sum(one.student == "NT")
n = 1000000
many.num.noturn = sapply(1:n,function(i){
	the.sample = sample( c("HW","None"), 40, replace = TRUE, prob = c(0.95,0.05))
	num.noturn = sum(the.sample == "None")
	return(num.noturn)
})
hist(many.num.noturn)
n = 1000000
many.num.noturn = sapply(1:n,function(i){
	the.sample = sample( c("HW","None"), 40, replace = TRUE, prob = c(0.95,0.05))
	num.noturn = sum(the.sample == "None")
	return(num.noturn)
})
table(many.num.noturn)
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
})
A = sum(many.students == "NT")
v.return = c(A/n,sd(many.students == "NT"))
names(v.return) = c("mean","standard deviation" )
v.return
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
  A = sum(one.student == "NT")
  return(A)
  })
sum(many.students == 0)/n
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
  A = sum(one.student == "NT")
  return(A)
  })
A = sum(many.students == 0)
B = sum(many.students == 1)
1-((A + B)/n)
n = 1000000
one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
many.students = sapply(1:n, function(i){
  one.student = sample(c("T","NT"), prob = c(0.95,0.05),40,replace = TRUE)
  A = sum(one.student == "NT")
  return(A)
  })
median(many.students)
lynx = as.numeric(lynx)
hist(lynx)
v.return = c(mean(lynx),var(lynx))
names(v.return) = c("mean","variance")
v.return
lynx = as.numeric(lynx)
the.sample = sample(lynx,10)
mean(the.sample)
n = 1000000
many.samples = sapply(1:n, function(i){
  lynx = as.numeric(lynx)
  the.sample = sample(lynx,10)
  A = mean(the.sample)
  return(A)
})
v.return = c(mean(many.samples),sd(many.samples))
names(v.return) = c("mean","standard deviation")
v.return
lynx = as.numeric(lynx)
n = 1000000
many.samples1 = sapply(1:n, function(i){
  the.sample1 = sample(lynx,50)
  A = mean(the.sample1)
  return(A)
})
v.return1 = c(mean(many.samples1),sd(many.samples1))
names(v.return1) = c("mean","standard deviation")
v.return1
many.samples2 = sapply(1:n, function(i){
  the.sample2 = sample(lynx,10)
  B = mean(the.sample2)
  return(B)
})
v.return2 = c((mean(many.samples1) - mean(many.samples2)),(sd(many.samples1) - sd(many.samples2)))
names(v.return2) = c("difference in mean","difference in standard deviation")
v.return2
lynx = as.numeric(lynx)
n = 1000000
many.samples1 = sapply(1:n, function(i){
  the.sample1 = sample(lynx,50)
  A = mean(the.sample1)
  return(A)
})
hist(lynx)
```