---
title: "STA 32 - HW7 "
author: "HANGSHI JIN"
output: html_document
---
  
### Problem I
### (a)
```{r, echo = FALSE}
crime <- read.csv("C:/Users/jinhangshi2008/Desktop/STA32/Dataset/crime.csv")
dip <- crime$dip
rate <- crime$rate
plot(rate ~ dip)
title("Linear Relationship between Crime Rate and Diploma")
```

### (b)
```{r, echo = FALSE}
A = lm(crime$rate ~ crime$dip)
plot(rate ~ dip)
title("Linear Relationship between Crime Rate and Diploma")
abline(A,lwd = 2)
```

### (c)
```{r, echo = FALSE}
round(A$coefficients[2],digits = 3)
```
#when the percentage with high school diploma increases by 1 percent, crime rate would be expected to decrease by 170.575 per 100000 residents.This problem does not have a practical interception.

### (d)
```{r, echo = FALSE}
summary(crime)
ifelse(crime$rate >= 8840 | crime$rate <= 5020 | crime$dip >= 82.25 | crime$dip <= 76,"Outliers","Not Outliers")
```

### Problem II
### (a)
```{r, echo = FALSE}
qqnorm(A$residuals)
qqline(A$residuals)
```
#It looks like not normally distributed because it presents as a straight line.

### (b)
```{r, echo = FALSE}
plot(A$fitted.values, A$residuals, xlab = "Fitted Values", ylab = "errors", main = "Checking for constancy of variance of the errors")
```
#Because of outliers, the variance of the errors is not constant.

### (c)
```{r, echo = FALSE}
confint(A, level = 0.95)
```
#we are 95% confident that when the percentage with high school diploma increases by 1 percent, crime rate would be expected to decrease by 170.575 per 100000 residents.

### (d)
```{r, echo = TRUE}
#Yes, because as crime$dip increases, intercept also increases.
```

## APPENDIX OF CODE
```
crime <- read.csv("C:/Users/jinhangshi2008/Desktop/STA32/Dataset/crime.csv")
dip <- crime$dip
rate <- crime$rate
plot(rate ~ dip)
title("Linear Relationship between Crime Rate and Diploma")
A = lm(crime$rate ~ crime$dip)
plot(rate ~ dip)
title("Linear Relationship between Crime Rate and Diploma")
abline(A,lwd = 2)
round(A$coefficients[2],digits = 3)
summary(crime)
ifelse(crime$rate >= 8840 | crime$rate <= 5020 | crime$dip >= 82.25 | crime$dip <= 76,"Outliers","Not Outliers")
qqnorm(A$residuals)
qqline(A$residuals)
plot(A$fitted.values, A$residuals, xlab = "Fitted Values", ylab = "errors", main = "Checking for constancy of variance of the errors")
confint(A, level = 0.95)
```