---
  title: "STA 32 - HW 1"
author: "HANGSHI JIN"
output: html_document
---
  
  ### Problem I
  ### (a)
  ```{r, echo = FALSE}
ErinsFitbit <- read.csv("C:/Users/jinhangshi2008/Desktop/STA32/ErinsFitbit.csv")
names(ErinsFitbit)
```

### (b)
```{r, echo = FALSE}
rownames(ErinsFitbit)
```

### (c)* `summary()`
```{r, echo = FALSE}
summary(ErinsFitbit)
```
#It gives the data analysis for numerical columns, while gives the numbers of the times each category appears for categorical columns.

### (d)
```{r, echo = FALSE}
#ErinsFitbit$Steps
mean(ErinsFitbit$Steps)
the.mean = mean(ErinsFitbit$Steps)
```

### Problem II
### (a)
```{r, echo = FALSE}
Z = aggregate(Steps ~ Day, data = ErinsFitbit, mean)
names(Z) = "mean"
Z
```

### (b)
```{r, echo = FALSE}
X = aggregate(Sleep ~ Day, data = ErinsFitbit, mean)
names(X) = "mean"
X
```

### (c)
```{r, echo = FALSE}
A = aggregate(Steps ~ Day, data = ErinsFitbit, sd)
names(A) = "sd"
A
```

### (d)
```{r, echo = FALSE}
B = aggregate(Sleep ~ Day, data = ErinsFitbit, sd)
names(B) = "sd"
B
```

### Problem III
### (a)
```{r, echo = FALSE}
fivenum(ErinsFitbit$Miles)
```
#this function returns minimum number, lower-hinge, median, upper-hinge, maximum number of a dataset.

### (b)
```{r, echo = FALSE}
table(ErinsFitbit$Day)
```
#this table shows the counts at each combination of factor levels of each day of a week 

### (c)
```{r, echo = FALSE}
Y = aggregate(Sleep ~ Month, data = ErinsFitbit, median)
names(Y) = "median"
Y
```

### (d)
```{r, echo = FALSE}
C = aggregate(Miles ~ Month, data = ErinsFitbit, median)
names(C) = "median"
C
```

### Problem IV
### (a)
```{r, echo = FALSE}
boxplot(Steps ~ Day, data = ErinsFitbit)
```
#Sunday is less active than the rest because its range is the shortest and its maximum number is less than others'.

### (b)
```{r, echo = FALSE}
boxplot(Sleep ~ Day, data = ErinsFitbit)
```
#Monday seems like to be less restful than the rest because it has the longest range among the others.
### (c)
```{r, echo = FALSE}

```

#There is one outlier on Saturday and Wednesday respectively, and there are three outliers on Sunday. 

### (d)
```{r, echo = FALSE}

```
#There is one outlier on Monday, Thursday, Saturday, and Sunday, respectively. There are two outliers on Friday.

## APPENDIX OF CODE
ErinsFitbit <- read.csv("C:/Users/jinhangshi2008/Desktop/STA32/ErinsFitbit.csv")
names(ErinsFitbit)
rownames(ErinsFitbit)
summary(ErinsFitbit)
#It gives the data analysis for numerical columns, while gives the numbers of the times each category appears for categorical columns.
mean(ErinsFitbit$Steps)
the.mean = mean(ErinsFitbit$Steps)
Z = aggregate(Steps ~ Day, data = ErinsFitbit, mean)
names(Z) = "mean"
Z
X = aggregate(Sleep ~ Day, data = ErinsFitbit, mean)
names(X) = "mean"
X
A = aggregate(Steps ~ Day, data = ErinsFitbit, sd)
names(A) = "sd"
A
B = aggregate(Sleep ~ Day, data = ErinsFitbit, sd)
names(B) = "sd"
B
fivenum(ErinsFitbit$Miles)
#this function returns minimum number, lower-hinge, median, upper-hinge, maximum number of a dataset.
table(ErinsFitbit$Day)
#this table shows the counts at each combination of factor levels of each day of a week 
Y = aggregate(Sleep ~ Month, data = ErinsFitbit, median)
names(Y) = "median"
Y
C = aggregate(Miles ~ Month, data = ErinsFitbit, median)
names(C) = "median"
C
boxplot(Steps ~ Day, data = ErinsFitbit)
#Sunday is less active than the rest because its range is the shortest and its maximum number is less than others'.
boxplot(Sleep ~ Day, data = ErinsFitbit)
#Monday seems like to be less restful than the rest because it has the longest range among the others.
#There is one outlier on Saturday and Wednesday respectively, and there are three outliers on Sunday. 
#There is one outlier on Monday, Thursday, Saturday, and Sunday, respectively. There are two outliers on Friday.
#Put all your code used above here. 
```